---
title: "My First Report"
author: "miriam"
format:
  html:
    embed-resources: true
---

## Welcome to your practice report

This is a **Quarto** document. It mixes ordinary writing with live code, so your
report and your analysis always stay in sync. When you click **Render**, Quarto
runs the code below and builds a finished HTML page.

Try it now: change `author: "Your Name"` in the header above to your own name,
then click **Render**.

## A first look at the data

The code chunk below reads a small practice dataset from the `data/` folder and
shows the first few rows.

```{r}
# My first R calculation
5 + 5
```

## A first chart

```{r}
# My second R calculation
10 + 10
```

## Your turn

- Add a sentence here describing what you notice in the chart.
- Render again and check that both your sentence and the chart appear.

When you are happy with the result, **commit and sync** your work (the Week 2
course page walks you through this), then submit your repository link on Canvas.

## My Notes
**I learned to launch a Codespace.I learned how to edit YAML. I learned how to use Markdown**